---
title: "Assigment3_Albuquerque"
author: "Simone Albuquerque"
date: "2/28/2021"
output: html_document
---

```{r Load Packages}
library(tidyverse)
library(ggplot2)
```

For a slope of 0-3% 

This R markdown will use 3 functions soil_intake, allow_surf_acc and Max_runtime to identify the precipitation rate when the max run time (time prior to creating runoff) of an irrigation system is 0. Case_when_IR will use the soil infiltration rate based on soil characteristics to find the   Allowable surface accumulation (inches). Then Max_runtime will identify the precipitation rate when the max run time is 0 given a fixed IR. 

```{r load function and create results table}
#call in functions
source("soil_intake.R") # from soil type evaluates Soil Intake Rate (in/hr) IR
source("allow_surf_acc.R") #from IR evaluates Allowable Surface accumulation (inches) ASA
source("R_max.R") #uses values derived above and precip to calc minutes of irrigation till runoff is generated per day
```

```{r Define Soil Intake and Allowable Surface Accumulation}
knitr::opts_chunk$set(echo = TRUE)
soil_class<- "clay" #set your soil class: clay, silty clay, clay loam, loam, sandy loam, loamy sand, sand

IR<- soil_intake(soil_class) #define IR
ASA<- Allow_surf_acc(IR) # define ASA

```

```{r Read in irrigation Data (or create dataset)}

# total range of irrigation possibilities in a 24 hour interval
ir_data <- runif(min = 0, max = 200, n = 500) # created datset of irrigation values ( minutes of irrigation per day)

r_max(ir_data, IR = IR, ASA = ASA, PR = 0) # ran function for minutes of irrigation till runoff is generated per day to find the number of days, base don irrigation data, runoff was generated

```

